---
title: 'Homework #6'
author: "Max Ruehle"
date: "4/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 25** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

```{r}
windows.options(width=10, height=10)
library(ggplot2)
library(dplyr)
library(tidyverse)

topdog <- readxl::read_xlsx('KIB - Best in Show (public).xlsx', sheet = 'Best in show full sheet', skip = 3) %>% select(Breed = `Dog breed`, Type = `American Kennel Club group`, Size = '..32', Score = `intelligence + longevity + ailments + 50% (purchase price + food costs + grooming score). highest possible score: 4.5`, Popularity = `pure breeds, American Kennel Club 2011`, Intelligence = `1 = easiest to train / learn new commands`)
topdog[topdog == 'no data'] <- NA
topdog <- topdog %>% mutate(Type = as.factor(Type), Size = as.factor(Size), Intelligence = as.numeric(Intelligence))
topdog$Size <- factor(topdog$Size, levels(topdog$Size)[c(3, 2, 1)])
topdog$Intelligence[topdog$Intelligence <= 40] <- 0
topdog$Intelligence[topdog$Intelligence > 40] <- 1
topdog <- topdog %>% subset(Intelligence <= 1) #This command just subsets all of the intelligence rows with a numeric variable, getting rid of the NA values which makes the plot cleaner
topdog <- topdog %>% mutate(Intelligence = as.factor(Intelligence))

#Since some column titles were off place on the Excel sheet, I selected the correct titles and renamed them for simplicity.
```


2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure need to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

```{r}
ggplot(topdog, aes(x = Score, y = Popularity, color = Type, size = as.numeric(Size), shape = Intelligence, label = Breed)) + geom_point() + geom_text(check_overlap = TRUE, size = 3, hjust = 1.05) + guides(size=guide_legend(title="Size"), shape=guide_legend(title="Intelligence")) + ggtitle('TopDog Plot')
```

In this plot, the Score of the dog is ranked on the x axis while the popularity is on the y axis. The different colors of the points represent the types of dogs. The size of the points correspond with the size of the dog, with 1 being small dogs, 2 being medium sized dogs, and 3 being large dogs. The shape of the points represents the dogs' intelligence: A score of 0 means they are in the lower 50% quartile while a 1 means they are in the upper 50% quartile. 

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlap!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 